### 2015-05-28 doc/manual/inputParameters.tex
Added to user manual

\section{The {\ttfamily resolutionParameters}~namelist}

@@

The resolution parameters each have 3 associated sfincsScan parameters
which are used for convergence scans ({\ttfamily scanType} = 1): {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}.
The first two of these set the range by which the associated resolution parameter is scaled
in a convergence scan. The {\ttfamily ...NumRuns} parameter sets the number of values tried in a
convergence scan. The code attempts to space the values evenly in a logarithmic
sense, as in Matlab's 'logspace' function. For example, the following settings\\
{\ttfamily
    Nxi = 20\\
!ss NxiMinFactor = 0.5\\
!ss NxiMaxFactor = 2.0\\
!ss NxiNumRuns = 3\\
}
would mean the values {\ttfamily Nxi} = 10, 20, and 40 would be tried in a convergence scan.
If you don't want to scan a variable in a convergence scan, set the associated
{\ttfamily ...NumRuns} parameter to 0, or do not include this parameter in the input file.
For each resolution parameter ({\ttfamily Ntheta}, {\ttfamily Nzeta}, {\ttfamily Nxi}, etc.), the value itself is read by
Fortran and so should not be preceded by {\ttfamily !ss}.  However the {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}
quantities are read by \sfincsScan~and so must be preceded by {\ttfamily !ss}

@@

{\ttfamily scanType} = 1:  Convergence scan. (Scan the parameters in the resolutionParameters namelist.)\\

@@

{\ttfamily scanType} = 5:  Scan radius, and at each radius, scan $E_r$.  Density and temperature profiles are again
 taken from the {\ttfamily profiles} file; see \path{sfincs/fortran/utils/profiles.XXX} for examples.\\

@@

>>>>

\section{The {\ttfamily resolutionParameters}~namelist}
\label{sec:resolutionParameters}

@@

@@

{\ttfamily scanType} = 1:  Resolution convergence scan. (Scan the parameters in the resolutionParameters namelist.)\\

@@

{\ttfamily scanType} = 5:  Scan radius, and at each radius, scan $E_r$.  Density and temperature profiles are again
 taken from the {\ttfamily profiles} file; see \path{sfincs/fortran/utils/profiles.XXX} for examples.
In this type of scan, \sfincsScan~creates a subdirectory for each value of minor radius, and a
{\ttfamily scanType} = 2 scan is run in each of these subdirectories.
\\

@@

\subsection{Parameters related only to {\ttfamily scanType} = 1 (resolution convergence scans).}

The resolution parameters discussed in section \ref{sec:resolutionParameters}
each have 3 associated \sfincsScan~parameters
which are used for convergence scans ({\ttfamily scanType} = 1): {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}.
The first two of these set the range by which the associated resolution parameter is scaled
in a convergence scan. The {\ttfamily ...NumRuns} parameter sets the number of values tried in a
convergence scan. The code attempts to space the values evenly in a logarithmic
sense, as in Matlab's 'logspace' function. For example, the following settings\\
{\ttfamily
    Nxi = 20\\
!ss NxiMinFactor = 0.5\\
!ss NxiMaxFactor = 2.0\\
!ss NxiNumRuns = 3\\
}
would mean the values {\ttfamily Nxi} = 10, 20, and 40 would be tried in a convergence scan.
If you don't want to scan a variable in a convergence scan, set the associated
{\ttfamily ...NumRuns} parameter to 0, or do not include this parameter in the input file.
For each resolution parameter ({\ttfamily Ntheta}, {\ttfamily Nzeta}, {\ttfamily Nxi}, etc.), the value itself is read by
Fortran and so should not be preceded by {\ttfamily !ss}.  However the {\ttfamily ...MinFactor}, {\ttfamily ...MaxFactor}, and {\ttfamily ...NumRuns}
quantities are read by \sfincsScan~and so must be preceded by {\ttfamily !ss}

\ssparam{NthetaMaxFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which \Ntheta~will be multiplied in a convergence scan.}

\ssparam{NthetaMinFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which \Ntheta~will be multiplied in a convergence scan.}

\ssparam{NthetaNumRuns}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum number of values of \Ntheta~which will be used in a convergence scan.  Only odd integers can be used
for \Ntheta, so the actual number of \Ntheta~values used in the scan may be less than {\ttfamily NthetaNumRuns}.}

\ssparam{NzetaMaxFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which \Nzeta~will be multiplied in a convergence scan.}

\ssparam{NzetaMinFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which \Nzeta~will be multiplied in a convergence scan.}

\ssparam{NzetaNumRuns}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum number of values of \Nzeta~which will be used in a convergence scan.  Only odd integers can be used
for \Nzeta, so the actual number of \Nzeta~values used in the scan may be less than {\ttfamily NzetaNumRuns}.}

\ssparam{NxiMaxFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which \Nxi~will be multiplied in a convergence scan.}

\ssparam{NxiMinFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which \Nxi~will be multiplied in a convergence scan.}

\ssparam{NxiNumRuns}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum number of values of \Nxi~which will be used in a convergence scan.  Only integers can be used
for \Nxi, so the actual number of \Nxi~values used in the scan may be less than {\ttfamily NxiNumRuns}.}

\ssparam{NxMaxFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which \Nx~will be multiplied in a convergence scan.}

\ssparam{NxMinFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which \Nx~will be multiplied in a convergence scan.}

\ssparam{NxNumRuns}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum number of values of \Nx~which will be used in a convergence scan.  Only integers can be used
for \Nx, so the actual number of \Nx~values used in the scan may be less than {\ttfamily NxNumRuns}.}

\ssparam{solverToleranceMaxFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which {\ttfamily solverTolerance} will be multiplied in a convergence scan.}

\ssparam{solverToleranceMinFactor}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which {\ttfamily solverTolerance} will be multiplied in a convergence scan.}

\ssparam{solverToleranceNumRuns}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Number of values of {\ttfamily solverTolerance} which will be used in a convergence scan.}

\ssparam{NLMaxFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum factor by which \NL~will be multiplied in a convergence scan.}

\ssparam{NLMinFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Minimum factor by which \NL~will be multiplied in a convergence scan.}

\ssparam{NLNumRuns}
{integer}
{Only when {\ttfamily collisionOperator} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 1.}
{Maximum number of values of \NL~which will be used in a convergence scan.  Only integers can be used
for \NL, so the actual number of \NL~values used in the scan may be less than {\ttfamily NLNumRuns}.}

\ssparam{NxPotentialsPerVthMaxFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Maximum factor by which {\ttfamily NxPotentialsPerVth} will be multiplied in a convergence scan.}

\ssparam{NxPotentialsPerVthMinFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Minimum factor by which {\ttfamily NxPotentialsPerVth} will be multiplied in a convergence scan.}

\ssparam{NxPotentialsPerVthNumRuns}
{integer}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Number of values of {\ttfamily NxPotentialsPerVth} which will be used in a convergence scan.}

\ssparam{xMaxMaxFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Maximum factor by which {\ttfamily xMax} will be multiplied in a convergence scan.}

\ssparam{xMaxMinFactor}
{real}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Minimum factor by which {\ttfamily xMax} will be multiplied in a convergence scan.}

\ssparam{xMaxNumRuns}
{integer}
{Only when {\ttfamily collisionOperator} = 0, {\ttfamily xGridScheme} $<$ 5, and \sfincsScan~is run with {\ttfamily scanType} = 1.
Since the recommended value of {\ttfamily xGridScheme} is 5, this parameter is basically obsolete.}
{Number of values of {\ttfamily xMax} which will be used in a convergence scan.}

\subsection{Parameters related only to {\ttfamily scanType} = 2 (scans of radial electric field).}

In this scan of the radial electric field, the values of electric field used
will always be uniformly (linearly) spaced.  
Notice that exactly 1 of the 4 variables {\ttfamily dPhiHatdpsiHatMax}, {\ttfamily dPhiHatdpsiNMax}, {\ttfamily dPhiHatdrHatMax}, and {\ttfamily dPhiHatdrNMax}
will be used, depending on\\
{\ttfamily inputRadialCoordinateForGradients}.
Similarly, exactly 1 of the 4 variables
{\ttfamily dPhiHatdpsiHatMin}, {\ttfamily dPhiHatdpsiNMin}, {\ttfamily dPhiHatdrHatMin}, and {\ttfamily dPhiHatdrNMin}
will be used.

\ssparam{NErs}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Number of values of radial electric field to consider in a scan.}

\ssparam{dPhiHatdpsiHatMax}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Maximum value of {\ttfamily dPhiHatdpsiHat} to use in the scan.}

\ssparam{dPhiHatdpsiHatMin}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Minimum value of {\ttfamily dPhiHatdpsiHat} to use in the scan.}

\ssparam{dPhiHatdpsiNMax}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 1 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Maximum value of {\ttfamily dPhiHatdpsiN} to use in the scan.}

\ssparam{dPhiHatdpsiNMin}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 1 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Minimum value of {\ttfamily dPhiHatdpsiN} to use in the scan.}

\ssparam{dPhiHatdrHatMax}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 2 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Maximum value of {\ttfamily dPhiHatdrHat} to use in the scan.}

\ssparam{dPhiHatdrHatMin}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 2 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Minimum value of {\ttfamily dPhiHatdrHat} to use in the scan.}

\ssparam{dPhiHatdrNMax}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 3 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Maximum value of {\ttfamily dPhiHatdrN} to use in the scan.}

\ssparam{dPhiHatdrNMin}
{real}
{Only when {\ttfamily inputRadialCoordinateForGradients} = 3 and \sfincsScan~is run with {\ttfamily scanType} = 2.}
{Minimum value of {\ttfamily dPhiHatdrN} to use in the scan.}

\subsection{Parameters related only to {\ttfamily scanType} = 3 (scans of an arbitrary input parameter).}

\ssparam{scanVariable}
{string. Must be of the fortran namelist parameters that takes an integer or real value. Case-insensitive.}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 3.}
{Name of the variable to scan in a {\ttfamily scanType} = 3 scan.}

\ssparam{scanVariableMax}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 3.}
{Maximum value of {\ttfamily scanVariable} to use in a {\ttfamily scanType} = 3 scan.}

\ssparam{scanVariableMin}
{real}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 3.}
{Minimum value of {\ttfamily scanVariable} to use in a {\ttfamily scanType} = 3 scan.}

\ssparam{scanVariableN}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 3.}
{Number of values of {\ttfamily scanVariable} to use in a {\ttfamily scanType} = 3 scan.}

\ssparam{scanVariableScale}
{string. Must be `linear', `lin', 'logarithmic', or 'log'}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 3.}
{Whether to space the values of {\ttfamily scanVariable} in a linear or logarithmic manner.
The settings `linear' and `lin' have identical behavior. 
The settings `logarithmic' and `log' have identical behavior.}

\subsection{Parameters related only to {\ttfamily scanType} = 4 or 5 (radial scans).}

Notice that exactly 1 of the 4 variables {\ttfamily psiHat\_max}, {\ttfamily psiN\_max}, {\ttfamily rHat\_max}, and {\ttfamily rN\_max}
will be used, depending on
{\ttfamily inputRadialCoordinate}.
Similarly, exactly 1 of the 4 variables
{\ttfamily psiHat\_min}, {\ttfamily psiN\_min}, {\ttfamily rHat\_min}, and {\ttfamily rN\_min}
will be used.

\ssparam{profilesScheme}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{How to specify the profiles of density, temperature, and (when  {\ttfamily scanType} = 5)
the range of radial electric field to consider.\\

{\ttfamily profilesScheme} = 1: Read a `{\ttfamily profiles}' file which contains the input profiles on a grid in one of the 4 available radial coordinates.\\

{\ttfamily profilesScheme} = 2: Read a `{\ttfamily profiles}' file which contains the input profiles expressed as polynomials in one of the 4 available radial coordinates.
}

\ssparam{Nradius}
{integer}
{Only when \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Maximum number of values of minor radius to consider in the scan.
Depending on {\ttfamily geometryScheme} and {\ttfamily VMECRadialOption},
it may be that only surfaces available in the magnetic equilibrium file will be
used, in which case fewer than {\ttfamily Nradius} radii may be used.}

\ssparam{psiHat\_max}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Maximum value of {\ttfamily psiHat} to use in the scan.}

\ssparam{psiHat\_min}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 0 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Minimum value of {\ttfamily psiHat} to use in the scan.}

\ssparam{psiN\_max}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 1 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Maximum value of {\ttfamily psiN} to use in the scan.}

\ssparam{psiN\_min}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 1 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Minimum value of {\ttfamily psiN} to use in the scan.}

\ssparam{rHat\_max}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 2 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Maximum value of {\ttfamily rHat} to use in the scan.}

\ssparam{rHat\_min}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 2 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Minimum value of {\ttfamily rHat} to use in the scan.}

\ssparam{rN\_max}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 3 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Maximum value of {\ttfamily rN} to use in the scan.}

\ssparam{rN\_min}
{real}
{Only when {\ttfamily inputRadialCoordinate} = 3 and \sfincsScan~is run with {\ttfamily scanType} = 4 or 5.}
{Minimum value of {\ttfamily rN} to use in the scan.}
